A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/cover_letter_for_resubmission.tex

      \item \label{R_E_P1} \blue{....................}

@@

      \BLnote{I do not understand/I cannot see the issue the editor is referring to here}

@@

@@

      \blue{\bf{Manuscript Title before Amendment:}}
      \begin{center}
        \blue{A Reduced Order Model for Permeability Fields Using Singular Value Decomposition (SVD)}
        \end{center}
      \blue{\bf{Manuscript Title after Amendment:}}
      \begin{center}
        \blue{A Reduced Order Model for Porous Media Flows which Couples Linear Regression with Principal Component Analysis (PCA) using Singular Value Decomposition (SVD) or Higer Order Singular Value Decomposition (HOSVD): Upscaling the Permeability Field for Multiphase Reservoir Flow Simulation}
      \end{center}
      \blue{\bf{Manuscript body before Amendment:}}\\
      \\
      \\
      \blue{\bf{Manuscript body after Amendment:}}\\
      \\
      \\

@@

        These changes remove the simplification and the authors also hope they answered the important questions that the reviewer implied remained unanswered. The authors remain willing to provide a direct answer to any unanswered questions which are explicitly stated.}

@@

      \item \label{R_R1_MissedNewDev_P1} \blue{The authors thank the reviewers for the comment, references to the papers mentioned by the reviwer have now been included in the amended manuscript. Some of these papers were originally excluded from the manuscript initially because they were not related to upscaling. In line with the author's response at \ref{R_R1_Novelty}, the difference between the work in those papers and the authors' work are highlighted to draw out the uniqueness of the current work}

@@

      \item \label{R_R1_CompEffort} \blue{..........}

@@

Further to the explanation provided in the response at \ref{R_R1_Novelty}, while PCA (with respect to SVD or HOSVD) and linear regression are not new, the authors believe that the manner in which they (\ie PCA and linear regression) have been combined and applied to achieve dimensionality reduction for the problem at hand is novel}

@@

      \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment. The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}

@@

      \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive. These have been reduced from 86 to the most relevant 9 \red{update the number 9 after including figures for the 3D simulations} (which are included in the manuscript). Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}

@@

      \item \label{R_R2_TooMuchSum_1} \blue{The authors thank the reviewer for the comment, as advised, the latter part of the introduction has been made brief. Additionally, the extensive details in the introduction section which was referred to has been moved to the section on "Model Description and Simulation Setup".}

@@

      \item \label{R_R2_NumFormulation_1} \blue{..........}

@@

      \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}

@@

      \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section has been moved to the appendix. Additionally, as mentioned in the response at \ref{R_R1_OverSimplification_P1}, a newly introduced section titled ``A brief Introduction to HOSVD'' was also moved to the appendix.}

@@

      \item \label{R_R2_TensorCorrection_1} \blue{The authors appreciate the reviewer's correction and apologizes for the oversight. Section 4.2.1 has now been properly edited}

@@

      \item \label{R_R2_GeomSetupAlgorithm_1} \blue{The authors thank the review for the feedback, starting the section directly on 2D simulation if only a 2D simulation is presented in the work. The recommended changes have been made and for completeness, some work on 3D simulations have now been included in the manuscript} \red{................response to creating algorimthm required.........}

@@

\encl{Cover\_letter\_for\_resubmission.pdf, Highlight\_revised.pdf, Manuscript\_sourceFiles(Makefile, Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.tex, article\_/figure1.tex, Pics Folder, references.bib, elsarticle.cls, elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"

>>>>

      \item \label{R_E_P1} \blue{We deduced that the comment was a request for reference list within the manuscript (where more than one reference is cited) to be rearranged in ascending and and for reference source document (\ie{reference.bib}) to contain only the materials cited. Both tasks have been completed, however, we remain willing to quickly correct any other issue we may have overlooked.}

@@

@@

        \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

@@

        These changes remove the simplification and the authors also hope they answered the important questions that the reviewer implied remained unanswered. The authors remain willing to provide a direct answer to any unanswered questions which are explicitly stated.}\\
        \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

      \item \label{R_R1_MissedNewDev_P1} \blue{The authors thank the reviewers for the comment, references to the papers mentioned by the reviwer have now been included in the amended manuscript. Some of these papers were originally excluded from the manuscript initially because they were not related to upscaling. In line with the author's response at \ref{R_R1_Novelty}, the difference between the work in those papers and the authors' work are highlighted to draw out the uniqueness of the current work}\\
        \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

      \item \label{R_R1_CompEffort} \blue{..........}\\
        \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

        Further to the explanation provided in the response at \ref{R_R1_Novelty}, while PCA (with respect to SVD or HOSVD) and linear regression are not new, the authors believe that the manner in which they (\ie PCA and linear regression) have been combined and applied to achieve dimensionality reduction for the problem at hand is novel}\\
        \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

   \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment. The Abstract, Introduction and Section 3 has been amended and clarity has been provided regarding the issue of novelty as discussed in the response at \ref{R_R1_Novelty} and \ref{R_R2_Novelty_1}}\\
     \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

         \item \label{R_R2_TooMuchFig_1} \blue{The authors thank the reviewer for the comment and acknowledge that the number of figure and plots were excessive. These have been reduced from 86 to the most relevant 12 (which are included in the manuscript). Additionally, the comments in the result section focus on the relevant figures included in the manuscript.}\\
           \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

   \item \label{R_R2_TooMuchSum_1} \blue{The authors thank the reviewer for the comment, as advised, the latter part of the introduction has been made brief. Additionally, the extensive details in the introduction section which was referred to has been moved to the section on "Model Description and Simulation Setup".}\\
     \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

   \item \label{R_R2_NumFormulation_1} \blue{..........}\\
     \blue{Please see the following sections in the tracked revised manuscript}
 \item \blue{.......}

@@

 \item \label{R_R2_TooDesc_1} \blue{The authors thank the reviewer for the comment, as suggested, this section has been moved to the section titled Introduction}\\
   \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

  \item \label{R_R2_SVDWellKnown_1} \blue{The authors thank the reviewer for the comment, as suggested this section has been moved to the appendix. Additionally, as mentioned in the response at \ref{R_R1_OverSimplification_P1}, a newly introduced section titled ``A brief Introduction to HOSVD'' was also moved to the appendix.}\\
    \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

  \item \label{R_R2_TensorCorrection_1} \blue{The authors appreciate the reviewer's correction and apologizes for the oversight. Section 4.2.1 has now been properly edited}\\
     \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

 \item \label{R_R2_GeomSetupAlgorithm_1} \blue{The authors thank the review for the feedback, the recommendations with regards to the 2D geometry discussion as been made. And, as suggested for 4.2.2 and 4.2.3 (now 4.1.2 and 4.1.3, respectively), the subsections have been amended to provides references for SVD (and HOSVD) as well as PCA. Additionally, the manuscript text has been re-worded so that the section previuosly referred to as 4.2.2 refers to algorithms at 4.1.3 and 5.1.3; and Section 4.2.3 (now 4.1.3) has been written as an algorithm}\\
   \blue{Please see the following sections in the tracked version of the revised manuscript}
 \item \blue{.......}

@@

\encl{Cover\_letter\_for\_resubmission.pdf,\\
  Highlight\_revised.pdf,\\
  Stochastic\_Upscaling\_UK\_AMM\_2018\_TrackedRevision.pdf,\\
  Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.pdf,\\
  Manuscript\_sourceFiles(Makefile,\\
  Stochastic\_Upscaling\_UK\_AMM\_2018\_revised.tex,\\
  article\_figure1.tex,\\
  Pics Folder,\\
  references.bib,\\
  elsarticle.cls,\\
  elsarticle-harv.bst)} % List your enclosed documents here, comment this out to get rid of the "encl:"
